### 2020-09-22 manuscript/manuscript.rmd
change Philippe2009 tree names

>>>>

branch_lengths = read.csv("../data_processed/tables/branch_lengths.tsv", header=TRUE, sep="\t")

branch_lengths$Clade =
    factor(
        branch_lengths$Clade,
        levels = c("Bilateria", "Cnidaria", "Placozoa", "Porifera", "Ctenophora", "Choanoflagellata"))

p=ggplot (branch_lengths, aes(x=Clade, y=branch_length, fill=Clade)) + geom_violin(trim=FALSE) + geom_boxplot(width=0.1) + theme_classic()+  labs(x="Clade", y = "Branch Lengths")

p+scale_fill_manual(values=c("#E6BEFF", "#911EB4", "#82D1F4", "#009E73", "#E69F00", "#4363D8"))

Bilateria_branch_mean = branch_lengths %>% filter(Clade=="Bilateria") %>% summarise(mean = mean(branch_length), n = n())
Porifera_branch_mean = branch_lengths %>% filter(Clade=="Porifera") %>% summarise(mean = mean(branch_length), n = n())
Ctenophora_branch_mean = branch_lengths %>% filter(Clade=="Ctenophora") %>% summarise(mean = mean(branch_length), n = n())

taxa_map=read_tsv("../reconciliation/taxonomy_info/taxon_table.tsv") %>% filter(original_matrix=="../considered_data/Whelan2017/strict.phy")
outgroup= taxa_map %>% filter (clade_assignment=="Choanoflagellida")
Bilateria= taxa_map %>% filter (clade_assignment=="Bilateria")
Cnidaria= taxa_map %>% filter (clade_assignment=="Cnidaria")
Placozoa= taxa_map %>% filter (clade_assignment=="Placozoa")
Porifera= taxa_map %>% filter (clade_assignment=="Porifera")
Ctenophora= taxa_map %>% filter (clade_assignment=="Ctenophora")

tree1= read.tree("../trees_new/iqtree/Whelan2017_strict.model_test.treefile")
tree1_rooted =  root(tree1, outgroup$relabelled_name, resolved.root=TRUE)
p1 = ggtree(tree1_rooted) +
  geom_cladelabel(node=90, label="Ctenophora", color="#E69F00") +
  geom_cladelabel(node=114, label="Porifera", color="#009E73") +
  geom_hilight(node=90, fill="#E69F00") +
  geom_hilight(node=114, fill="#009E73") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 100)) + ggtitle("    WAG+C60")

tree2=read.tree("../trees_new/sensitive/Whelan2017_strict.phy_Poisson_CAT60.con.tre")
tree2_rooted =  root(tree2, outgroup$relabelled_name, resolved.root=TRUE)
p2= ggtree(tree2_rooted) +
  geom_cladelabel(node=119, label="Ctenophora", color="#E69F00") +
  geom_cladelabel(node=100, label="Porifera", color="#009E73") +
  geom_hilight(node=119, fill="#E69F00") +
  geom_hilight(node=100, fill="#009E73") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 100)) + ggtitle("    Poisson+nCAT60")

tree3=read.tree("../trees_new/sensitive/Whelan2017_strict.phy_Poisson_CAT90.con.tre")
tree3_rooted =  root(tree3, outgroup$relabelled_name, resolved.root=TRUE)
p3=ggtree(tree3_rooted) +
  geom_cladelabel(node=100, label="Ctenophora", color="#E69F00") +
  geom_cladelabel(node=130, label="Porifera", color="#009E73") +
  geom_hilight(node=100, fill="#E69F00") +
  geom_hilight(node=130, fill="#009E73") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 100)) + ggtitle("    Poisson+nCAT90")
p3 = flip(p3, 100, 98)

tree4=read.tree("../trees_new/phylobayes/Whelan2017_strict.bpcomp.con.tre")
tree4_rooted =  root(tree4, outgroup$relabelled_name, resolved.root=TRUE)
p4=ggtree(tree4_rooted) +
  geom_cladelabel(node=100, label="Ctenophora", color="#E69F00") +
  geom_cladelabel(node=130, label="Porifera", color="#009E73") +
  geom_hilight(node=100, fill="#E69F00") +
  geom_hilight(node=130, fill="#009E73") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 100)) + ggtitle("    Poisson+CAT")
p4 = flip(p4, 100, 98)

tree5=read.tree("../trees_new/phylobayes/Whelan2017_strict.phy_GTR_CAT.con.tre")
tree5_rooted =  root(tree5, outgroup$relabelled_name, resolved.root=TRUE)
p5=ggtree(tree5_rooted) +
  geom_cladelabel(node=119, label="Ctenophora", color="#E69F00") +
  geom_cladelabel(node=100, label="Porifera", color="#009E73") +
  geom_hilight(node=119, fill="#E69F00") +
  geom_hilight(node=100, fill="#009E73") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 100)) + ggtitle("    GTR+CAT")

ggarrange(p1, p2, p3, p4, p5,  ncol  = 3, nrow = 2, labels = c("A", "B", "C", "D" , "E"), common.legend = TRUE)
